Simulation of Raman sideband cooling with large Lamb-Dicke factor and high initial temperature

### 2014-05-13 report/paper.tex
[report] intro

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}
Sideband cooling is a powerful technique for cooling confined particles, especially for ions in ion traps, to their ground states in both external and internal degrees of freedom. One of its variation, is also used in some experiment for cooling neutral atoms confined in an optical lattice\cite{sideband-cs-lattice} or a tightly focused tweezer optical dipole trap\cite{sideband-single-jila,sideband-single-cua}. Due to the heating from photon scattering, most of these experiments requires the particle to be confined to much smaller than an optical wavelength. Although this is possible to do for heavy atoms, e.g. Rubidium and Cesium, or ions, it is hard to get the same confinement for lighter neutral atoms like sodium.

>>>>

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Sideband cooling is a powerful technique for cooling confined particles, especially for ions in ion traps, to their ground states in both external and internal degrees of freedom. One of its variation, is also used in some experiment for cooling neutral atoms confined in an optical lattice\cite{sideband-cs-lattice} or a tightly focused tweezer optical dipole trap\cite{sideband-single-jila,sideband-single-cua}. Due to the heating from photon scattering, most of these experiments requires the particle to be confined to much smaller than an optical wavelength. Although this is possible to do for heavy atoms, e.g. Rubidium and Cesium, or ions, it is hard to get the same confinement for lighter neutral atoms like sodium.\\

However, although the heating from optical pumping is faster with looser confinement, the strength of Raman transition to vibrational states much more than one level lower also increases ($\delta n\gg1$), which raise the possibility of faster cooling by driving Raman transition to take away more than one quanta of vibrational energy ($\hbar\omega$). In this paper, I am going to study the possibility of such cooling scheme using numerical stimulations and show that with carefully optimized cooling sequence, one can use this method to cool atoms with a relatively loose confinement and high initial temperature to its low vibrational states.

\section{Theory of Raman sideband cooling}
